Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-20 article.tex
reshuffling of results!

How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
Results: Use the agreed upon definitions to fully realise factors and their impact.

@@

The key factors identified were defined as shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to environmental sustainability was assessed. The definitions provided a clear framework for measurement, ensuring that the factors could be consistently evaluated.

The quantification of each factor allowed for a systematic analysis of their impacts. For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact. Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).

By applying these definitions, the study effectively translated the qualitative aspects of environmental sustainability into usable metrics. This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships.

The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving environmental sustainability; allowing each factor's contribution to be clearly understood and relationships  explicitly defined.

\subsection{Comparative Analysis of Literature and Industry Perspectives}
    What are the factors of environmental sustainability in the Australian winegrowing industry?
        Purpose: Explore and understand the both the literature and industry perspectives on this.
        Results Literature review. Industry list of factors. Mind Map? Leximancer network.
        - Use the same words as the definitions in the search to show the parralels and differences.

        TODO: write a summary description of the leximancer outputs.

\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

@@

@@

In this case study, we apply BN to model and analyze the complex interactions between various environmental factors affecting wine production in Coonawarra. By incorporating industry-specific data and expert knowledge, the BN framework allows us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other. This approach not only aids in understanding the current sustainability status of the region but also helps in identifying potential areas for improvement and implementing effective management strategies.

The insights gained from this case study can serve as a valuable reference for other winegrowing regions aiming to enhance their environmental sustainability practices through the use of advanced probabilistic models like Bayesian Networks.

@@

\begin{figure}[h!]
    \centering
    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}
    \label{fig:coonawarra_bn}
  \end{figure}

@@

  This subsection examines how the identified key factors impacting environmental sustainability vary across different wine regions in Australia, with a focus on Coonawarra. By comparing the generic Bayesian Network (BN) model to the Coonawarra-specific model (Figure \ref{fig
  } and Figure \ref{fig
  }), we identify regional characteristics that influence these variations.

The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel. The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies. It is important to acknowledge that this analysis also illustrates that further work would be required to describe other regions or specific vineyards.

The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact. For instance, the Coonawarra-specific model demonstrates that the significance that pest/disease, and agrochemicals have a higher sensitivity to environmental impact compared factors such as green house gas emissions. Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target.

By using Conditional Probability Tables (CPTs) within the BN, the significant contributions of different variables to environmental sustainability in Coonawarra were assessed. Figures \ref{fig
  } and \ref{fig
  } illustrate these networks with nodes coloured according to their sensitivity values relative to environmental impact.

In the Coonawarra-specific BN, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions. These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.

The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management and tractor passes. In one, more tractor passes were used purposefully to manage the vineyard floor; the other managed vineyard floor as a consequence of tractor passes, leveraging opportunities when the tractor was used. This distinction highlights how operational decisions can vary based on regional practices and priorities. A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land. However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.

As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture. The edges between different factors reveals that water is the most connected. Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.

@@

>>>>

% How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
% Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
% Results: Use the agreed upon definitions to fully realise factors and their impact.

@@

The key factors identified were defined as shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed. The quantification of each factor allowed for a systematic assessment of their impacts. For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact. Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).

By applying these definitions, the study effectively translated the qualitative aspects of environmental sustainability into usable metrics. This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships. The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving environmental sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined. This was key within the construction of the BN, were the industry panel could easily refer to the specifics of each definition and thus how it might relate to other factors.

\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}

    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

@@

\subsection{Comparative Analysis of Literature and Industry Perspectives}
    % What are the factors of environmental sustainability in the Australian winegrowing industry?
    %     Purpose: Explore and understand the both the literature and industry perspectives on this.
    %     Results Literature review. Industry list of factors. Mind Map? Leximancer network.
    %     - Use the same words as the definitions in the search to show the parralels and differences.

@@

Identified key factors impacting environmental sustainability were examined with regard to Coonawarra. By comparing the generic Bayesian Network (Figure \ref{fig:b}) model to the Coonawarra-specific model (Figure \ref{fig:robyn} and Figure \ref{fig:marcel}), we identified regional characteristics that influence these variations. In this case study, we altered the general Australian BN to model and analyse the complex interactions between various environmental factors affecting wine production in Coonawarra. By incorporating industry-specific data and expert knowledge, the BN framework allowed us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other. This approach not only aids in understanding the current sustainability status of the region but also helps in identifying potential areas for improvement and implementing effective management strategies. The resultant two models represent the final consensus, reflecting the diverse perspectives and occasionally differing viewpoints among the experts, necessitating the development of two distinct but complementary models.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{robyn}
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:robyn}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{marcel}
    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:marcel}
\end{figure}

@@

The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel. Figure \ref{fig:robyn} and \ref{fig:marcel} highlight the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies. It is important to acknowledge that this analysis also illustrates that further work would be required to describe other regions or specific vineyards.

The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management and tractor passes. In one, greater tractor passes were used purposefully to manage the vineyard floor; the other managed vineyard floor as a consequence of tractor passes, leveraging opportunities when the tractor was used. This distinction highlights how operational decisions can vary based on regional practices and priorities. A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land. However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.

As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture. The edges between different factors reveals that water is the most connected. Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.Within both of the models, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions. These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.

The influence of factors on each other are described through the CPT values (see appendix) and allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact. For instance, the significant sensitivity that environmental impact had with regard to pests/disease, climate and agrochemicals compared to factors such as green house gas emissions. Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target. Furthermore, the relationships help to illustrate the further complexity of how these significant factors relate to these further considerations such as greenhouse gas emissions and the extended connection to fuel or electricity use. Where addressing issues such as disease can require the increased use of tractors and thus fuel.

@@

\section{}
